
```{r}
sages_mr <- readRDS(file=fs::path(r_objects_folder, "015_sages_mr.rds"))
sages_mr_pre_imp <- readRDS(file=fs::path(r_objects_folder, "015_sages_mr_pre_imp.rds"))
covariates_excessive_missing_labs <- readRDS(file=fs::path(r_objects_folder, "015_covariates_excessive_missing_labs.rds"))

```

# Summary of lab values

## Missing values

These are the lab values that were dropped for having more than 50% missing values:

```{r}

sages_mr_pre_imp %>%
  select(all_of(covariates_excessive_missing_labs)) %>%
  gtsummary::tbl_summary()

```

Imputation was done on the remaining lab values using predictive mean matching.

<!-- This will insert a page break  -->

```{=openxml}
<w:p><w:r><w:br w:type="page"/></w:r></w:p>
```

## Indicator variables

Indicator variables for low and high values were created for the lab values. 

This section provides summary statistics of whether the lab values met a clinically relevant cutoff.

## Pre-op labs

### Pre-op labs - any abnormality

Note: BUN/CRE ratio and Anion Gap thresholds were not updated and used values from previous work.

```{r}
sages_mr %>%
  select(starts_with("lab")) %>%
  select(dplyr::contains(".1.")) %>%
  select(ends_with("abnormal")) %>%
gtsummary::tbl_summary()

```


<!-- This will insert a page break  -->

```{=openxml}
<w:p><w:r><w:br w:type="page"/></w:r></w:p>
```

### POD1 labs

```{r}
sages_mr %>%
  select(starts_with("lab")) %>%
  select(dplyr::contains(".2.")) %>%
  select(ends_with("abnormal")) %>%
gtsummary::tbl_summary()

```

<!-- This will insert a page break  -->

```{=openxml}
<w:p><w:r><w:br w:type="page"/></w:r></w:p>
```

### POD2 labs

```{r}
sages_mr %>%
  select(starts_with("lab")) %>%
  select(dplyr::contains(".3.")) %>%
  select(ends_with("abnormal")) %>%
gtsummary::tbl_summary()

```


