
<!-- This will insert a page break  -->

```{=openxml}
<w:p><w:r><w:br w:type="page"/></w:r></w:p>
```

# Variable reduction

This section details the variable reduction technique from Harrell's Regression Modeling Strategies that we used to reduce the number of variables used in the analysis.


The data was split into training (80%) and testing (20%) sets.

```{r}
sages_juiced_rms <- readRDS(file=fs::path(r_objects_folder, "060_sages_juiced_rms.rds"))
sages_reduced <- readRDS(file=fs::path(r_objects_folder, "060_sages_reduced.rds"))
sages_combined <-   readRDS(file=fs::path(r_objects_folder, "020_sages_combined.rds"))
variable_df <- readRDS(file=fs::path(r_objects_folder, "021_variable_df.rds"))

covariates_to_use <- variable_df %>%
  filter(covariates_to_use_2) %>%
  pull(covariates_all)
covariates_to_use <- covariates_to_use[!covariates_to_use %in% c("vdsagesdeliriumever", "vdgcp_slope36m", "vdgcp_slope48m")]
sages_combined <- sages_combined %>%
  select(any_of(covariates_to_use))

```


```{r}
covariates_dropped_nzv <- names(sages_combined)[!(names(sages_combined) %in% names(sages_juiced_rms))]
covariates_not_dropped_nzv <- names(sages_combined)[(names(sages_combined) %in% names(sages_juiced_rms))]
```

<!-- This will insert a page break  -->

```{=openxml}
<w:p><w:r><w:br w:type="page"/></w:r></w:p>
```

Of the `r length(covariates_to_use)` variables we start with, we dropped `r length(covariates_dropped_nzv)` of them for not having a lot of variability.

These are the variables that were dropped:

```{r}
sages_combined %>%
  select(all_of(covariates_dropped_nzv)) %>%
  gtsummary::tbl_summary()
```

```{r}
covariates_dropped_rms <- names(sages_juiced_rms)[!(names(sages_juiced_rms) %in% names(sages_reduced))]
covariates_not_dropped_rms <- names(sages_juiced_rms)[(names(sages_juiced_rms) %in% names(sages_reduced))]
```

<!-- This will insert a page break  -->

```{=openxml}
<w:p><w:r><w:br w:type="page"/></w:r></w:p>
```
 
Of the `r length(covariates_not_dropped_nzv)` variables retained, `r length(covariates_dropped_rms)` were dropped due to redundancy.

These are the variables that were dropped:

```{r}
sages_combined %>%
  select(all_of(covariates_dropped_rms)) %>%
  gtsummary::tbl_summary()
```

<!-- This will insert a page break  -->

```{=openxml}
<w:p><w:r><w:br w:type="page"/></w:r></w:p>
```

### List of predictive features after dropping for missingness, low variance, and redundancy:

There are `r length(covariates_not_dropped_rms)` variables retained after the redundancy analysis.

```{r}
sages_combined %>%
  select(any_of(covariates_not_dropped_rms)) %>% 
  labelled::var_label() %>%
  as_tibble() %>%
  pivot_longer(everything(), names_to = "variable", values_to = "label") %>%
  gt::gt()
```



