
<!-- This will insert a page break  -->

```{=openxml}
<w:p><w:r><w:br w:type="page"/></w:r></w:p>
```

# Variable reduction (delirium prediction)

This section details the variable reduction technique from Harrell's Regression Modeling Strategies that we used to reduce the number of variables used in the analysis.



```{r}
sages_juiced_rms <- readRDS(file=fs::path(r_objects_folder, "0680_sages_juiced_rms.rds"))
sages_reduced <- readRDS(file=fs::path(r_objects_folder, "080_sages_reduced.rds"))
sages_combined <-   readRDS(file=fs::path(r_objects_folder, "022_sages_combined.rds"))
variable_df <- readRDS(file=fs::path(r_objects_folder, "021_variable_df.rds"))

covariates_to_use <- variable_df %>%
  filter(covariates_to_use_4) %>%
  pull(covariates_all)
covariates_to_use <- covariates_to_use[!covariates_to_use %in% c("vdsagesdeliriumever", "vdgcp_slope36m", "vdgcp_slope48m", "vdgcp_slope72m")]
sages_combined <- sages_combined %>%
  select(any_of(covariates_to_use))

```


```{r}
covariates_dropped_nzv <- names(sages_combined)[!(names(sages_combined) %in% names(sages_juiced_rms))]
covariates_not_dropped_nzv <- names(sages_combined)[(names(sages_combined) %in% names(sages_juiced_rms))]
```

<!-- This will insert a page break  -->

```{=openxml}
<w:p><w:r><w:br w:type="page"/></w:r></w:p>
```

Of the `r length(covariates_to_use)` variables we start with, we dropped `r length(covariates_dropped_nzv)` of them for having a low amount of variability.

These are the variables that were dropped:

```{r}
sages_combined %>%
  select(all_of(covariates_dropped_nzv)) %>%
  gtsummary::tbl_summary(
    statistic = list(
      all_continuous() ~ "{mean} ({sd})"),
    type = all_dichotomous() ~ "categorical"
  )
```

```{r}
covariates_sages_juiced <- names(sages_juiced_rms)
covariates_sages_juiced <- covariates_sages_juiced[!covariates_sages_juiced %in% c("vdsagesdeliriumever", "vdgcp_slope36m", "vdgcp_slope48m")]
covariates_dropped_rms <- covariates_sages_juiced[!(covariates_sages_juiced %in% names(sages_reduced))]
covariates_not_dropped_rms <- covariates_sages_juiced[(covariates_sages_juiced %in% names(sages_reduced))]
```

<!-- This will insert a page break  -->

```{=openxml}
<w:p><w:r><w:br w:type="page"/></w:r></w:p>
```
 
Of the `r length(covariates_not_dropped_nzv)` variables retained, `r length(covariates_dropped_rms)` were dropped due to redundancy.

These are the variables that were dropped:

```{r}
sages_combined %>%
  select(all_of(covariates_dropped_rms)) %>%
  gtsummary::tbl_summary(
    statistic = list(
      all_continuous() ~ "{mean} ({sd})"),
    type = all_dichotomous() ~ "categorical"
  )
```

<!-- This will insert a page break  -->

```{=openxml}
<w:p><w:r><w:br w:type="page"/></w:r></w:p>
```

### List of predictive features after dropping for missingness, low variance, and redundancy:

There are `r length(covariates_not_dropped_rms)` variables retained after the redundancy analysis.

```{r}
sages_combined %>%
  select(all_of(covariates_not_dropped_rms)) %>% 
  labelled::var_label() %>%
  as_tibble() %>%
  pivot_longer(everything(), names_to = "variable", values_to = "label") %>%
  gt::gt()
```



